%% An Example Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{filecontents}{parapub.bib}
@article{Hostettler2014,
    author = {Hostettler, Roland},
    title = {Parallel Publishing Toolbox},
    month = {April},
    year = {2014},
    journal = {Transactions on LaTeX Packages},
    number = {1},
    volume = {1}
}
\end{filecontents}

%% Example/Documentation Start %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,oneside,11pt]{article}
% Use UTF-8
\usepackage[utf8]{inputenc}

% Make nicer page margins
\usepackage{geometry}

% For the bibilography above
\usepackage{filecontents}

% For source code
\usepackage{verbatim}

% Make the items look nicer
\usepackage{enumitem}
\setlist[itemize]{leftmargin=2.5cm}

% Use paragraph skip instead of paragraph indentation
%\usepackage{parskip}

% Include the parapub package
\usepackage{parapub}
%\usepackage[nohyperref]{parapub}

% Title
\title{Parallel Publishing Toolbox}
\author{Roland Hostettler}
\date{\today}

\begin{document}

%% Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Insert disclaimer
\disclaimer{title=Parallel Publishing Toolbox,author=Roland Hostettler,citekey=Hostettler2014,journal={Transactions on LaTeX Packages},doi={AA.BBB/CCC.DDD.EEE},copyright={\copyright\ 2014 The Royal LaTeX Society.},published}

% Add title
\maketitle

% A quick abstract
\abstract{Many publishers allow parallel publishing of scientific articles for non-profit on the employers and/or sponsors website and this practice is also endorsed by LTU in an attempt to increase visibility. When doing this, publishers normally require you to add a proper copyright statement including a full citation of the true article and the article's DOI. This package helps achieving that by adding an extra frontpage to the article with just one command, hence keeping the extra work required minimal.}

%% Documentation %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Package Loading and Options}
The package is loaded using regular \LaTeX syntax, that is, using
%
\begin{verbatim}
	\usepackage[<options>]{parapub}
\end{verbatim}

The following \texttt{<options>} can be specified:
%
\begin{itemize}
	\item[\texttt{nohyperref}] By default, the DOI is a clickable hyperlink and takes the reader directly to the article. This requires the \texttt{hyperref} package which also makes references, etc.\ clickable which in turn might cause problems with certain document classes. Specifying the package option \texttt{nohyperref} disables the hyperlinks and prevents \texttt{hyperref} from loading.
\end{itemize}


\section{Adding a Disclaimer}
A disclaimer page is added using the
%
\begin{verbatim}
	\disclaimer{<info>}
\end{verbatim}
%
command issued \textbf{before} \verb|\maketitle|. In order for the frontpage to carry the necessary information it has to be passed to the \verb|\disclaimer{}| command. This is done using key-value pairs. There are two sets of information that has to be supplied. First, for preprints that have not yet been accepted or published, the following format is used:
%
\begin{verbatim}
	\disclaimer{title=Parallel Publishing Toolbox,author=Roland
	    Hostettler,journal={Transactions on LaTeX Packages},preprint}
\end{verbatim}

Here, the individual keys are:
%
\begin{itemize}
	\item[\texttt{title}]     The paper title (in a future version, this might be taken from the document info automatically).
	
	\item[\texttt{author}]    The paper author(s) (in a future version, this might be taken from the document info automatically).
	
	\item[\texttt{journal}]   The journal or conference the paper has been sent to.
	
	\item[\texttt{preprint}]  To indicate that it is a preprint paper.
\end{itemize}

For an accepted or published paper, the following format should be used:
%
\begin{verbatim}
	\disclaimer{title=Parallel Publishing Toolbox,author=Roland
	   Hostettler,journal={Transactions on LaTeX Packages},
	   citekey=Hostettler2014,,doi={AA.BBB/CCC.DDD.EEE},
	   copyright={\copyright\ 2014 The Royal LaTeX Society.},published}
\end{verbatim}

Here, in addition to the same keys used in the first case (\texttt{title}, \texttt{author}, and \texttt{journal}) the following keys are required:
%
\begin{itemize}
	\item[\texttt{citekey}]    A key to the citation of the paper in the bibliography which will include the full citation on the front page and instructions on how to cite the document.

	\item[\texttt{doi}]        The paper DOI which will be used for generating a link to the document and be included on the front page.
	
	\item[\texttt{copyright}]  A copyright notice which is usually provided by the publisher (see also Section~\ref{sec:copyright_notices} below).
	
	\item[\texttt{published}]  Used instead of \texttt{preprint}.
\end{itemize}


\section{Predefined Copyright Notices}
\label{sec:copyright_notices}
Publishers often supply a predefined copyright notice that has to appear on preprints and/or parallel published versions of accepted/published papers. Some of them are included in the toolbox and can be accessed through commands. The currently implemented notices are:
%
\begin{itemize}[leftmargin=4.5cm]
	\item[\texttt{\textbackslash IEEECopyrightNotice}]	Default IEEE copyright notice.
\end{itemize}


%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{parapub.bib}

\end{document}

